\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2022-02-01 main.tex
Updates from Overleaf

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{examples/images/xlarge-dz-dr.pdf}
    \caption{\SuperScreen results may be unreliable for multi-layer models where the spacing between layers is smaller than the typical vertex-to-vertex distance, $\delta r$. ({\bf a}) Field coil - pickup loop mutual inductance for the largest SQUID suscepometer modeled in Section~\ref{section:examples:scanning-squid} as a function of the minimum vertical spacing between layers, $\delta z$. The simulated mutual inductance is shown with blue circles, and a histogram of the mesh vertex-to-vertex distances $\delta r$ is shown in orange (arb. $y$ axis units). When $\delta z\lesssim\delta r$, the model significantly overestimates the mutual inductance. ({\bf b}) and ({\bf c}): Out-of-plane magnetic field $\mu_0H_z$ evaluated at the plane of the pickup loop (W1 layer) for ({\bf b}) the nominal layer spacing with $\delta z<\delta 2$ (indicated with a black $\times$ in ({\bf a})) and ({\bf c}) $\delta z > \delta r$ (indicated with a black $+$ in ({\bf a})). For $\delta r\lesssim\delta z$, the magnet field calculated using Eq.~\ref{eq:hz-from-kernel} resembles that of a discrete set of isolated dipoles rather than a continuous sheet of current.}
    \label{fig:xlarge-dz-dr}
\end{figure}

>>>>

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{examples/images/xlarge-dz-dr.pdf}
    \caption{\SuperScreen results may be unreliable for multi-layer models where the spacing between layers is smaller than the typical vertex-to-vertex distance, $\delta r$. ({\bf a}) Field coil - pickup loop mutual inductance for the largest SQUID suscepometer modeled in Section~\ref{section:examples:scanning-squid} as a function of the minimum vertical spacing between layers, $\delta z$. The simulated mutual inductance is shown with blue circles, and a histogram of the mesh vertex-to-vertex distances $\delta r$ is shown in orange (arb. $y$ axis units). When $\delta z\lesssim\delta r$, the model significantly overestimates the mutual inductance. ({\bf b}) and ({\bf c}): Out-of-plane magnetic field $\mu_0H_z$ evaluated at the plane of the pickup loop (W1 layer) for ({\bf b}) the nominal layer spacing with $\delta z<\delta 2$ (indicated with a black $\times$ in ({\bf a})) and ({\bf c}) $\delta z > \delta r$ (indicated with a black $+$ in ({\bf a})). For $\delta r\lesssim\delta z$, the magnet field calculated using Eq.~\ref{eq:hz-from-kernel} resembles that of a discrete set of isolated dipoles rather than a continuous sheet of current. Note that ({\bf b}) and ({\bf c}) share the same color scale, which is saturated in ({\bf b}).}
    \label{fig:xlarge-dz-dr}
\end{figure}
